### 2020-08-27 cases_and_policies/rmd/regressionsWithPlots.Rmd
Committing changes before mergning master.

---
title       : "Causal impact of masks, policies, behavior on early COVID-19 pandemic in the U.S."
subtitle    : "Tables and Figures"
author      :  Victor Chernozhukov, Paul Schrimpf, Hiro Kasahara
job         :
date        : "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "covid.bib"
link-citations: true
always_allow_html: true
output      :
    html_document :
        toc : true
        toc_depth : 3
        toc_float : true
        number_sections : true
        #theme : journal
        #css : 628notes.css
        code_folding: hide
        #lib_dir : deps
        self_cononontained : true
        fig_width: 8
        fig_height: 6
---

@@

sgtype <- opts_knit$get("rmarkdown.pandoc.to")
sgstyle <- 'default'
colors <-  scale_color_solarized
colors_fill <- scale_fill_solarized
rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
rootdir <- "/Users/Hiro/Documents/GitHub/covid-impact" 
source(paste(rootdir,"cases_and_policies/R/exploratory.R", sep="/"))
source(paste(rootdir,"cases_and_policies/R/dataprep.R",sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/varlabels.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/regprep.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/generatetables.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/bootstrap_felm.R", sep="/"))

@@

```{r testsmooth, cache=FALSE}
rearrange <- function(x, id) {
  for (i in unique(id)) {
    xi <- x[id==i]
    xi[!is.na(xi)] <- sort(xi[!is.na(xi)])
    x[id==i] <- xi
  }
  return(x)
}

dropnotincreasing <- function(x, id, t) {
  const <- (x <= panellag(x, id, t))
  const[is.na(const)] <- FALSE
  x[const & x>0] <- NA
  return(x)
}

lininterp <- function(x, id, t) {
  for (i in unique(id)) {
    xi <- x[id==i]
    ti <- t[id==i]
    xi[is.na(xi)] <- approx(ti[!is.na(xi)], xi[!is.na(xi)], ti[is.na(xi)])$y
    x[id==i] <- xi
  }
  return(x)
}

smoothtests <- function(x, id, t) {
  x[is.na(x)] <- 0
  return(lininterp(dropnotincreasing(rearrange(x,id),id,t),id,t))
}

df$neg.interp <- smoothtests(df$negative, df$state, df$date)
df$pos.interp <- df$cases #smoothtests(df$positive, df$state, df$date)
df$tot.interp <- df$neg.interp + df$pos.interp

L <- 7
df$tests <- paneldiff(df$tot.interp, df$state, df$date, lag=L)
df$testrate  <- df$tests/df$Population.2018*1000
df$testrate[df$testrate<0] <- NA
df$dlogtests <- paneldiff(log(sapply(df$testrate, function(x)
  max(x,exp(-1)))), df$state, df$date, lag=L)
df$testratedc <- df$ddeath/df$dcases*df$testrate
df$testratedc[df$dcases==0] <- 0

df$tests.ma <- paneldiff(panelma(df$neg.interp, df$state, df$date, 7) + df$cases,
                         df$state, df$date, lag=L)
df$testrate.ma  <- df$tests.ma/df$Population.2018*1000
df$testrate.ma[df$testrate.ma<0] <- NA
df$dlogtests.ma <- paneldiff(log(sapply(df$testrate.ma, function(x)
  max(x,exp(-1)))), df$state, df$date, lag=L)
df$testratedc.ma <- df$ddeath/df$dcases*df$testrate.ma
df$testratedc.ma[df$dcases==0] <- 0

df$logtests <- log(sapply(df$testrate, function(x)
  max(x,exp(-1))))

df$lagtests <- panellag(df$dlogtests, df$state, df$date, lag=1)  
df$dlogtests[is.na(df$dlogtests)] <- df$lagtests[is.na(df$dlogtests)]

@@

## DML 
```{r regsdml,  eval = TRUE, cache=FALSE, warning=FALSE, results='asis'}

>>>>

---
title       : "Causal impact of masks, policies, behavior on early COVID-19 pandemic in the U.S."
subtitle    : "Tables and Figures"
author      :  Victor Chernozhukov, Paul Schrimpf, Hiro Kasahara
job         :
date        : "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "covid.bib"
link-citations: true
always_allow_html: true
output      :
    html_document :
        toc : true
        toc_depth : 3
        toc_float : true
        number_sections : true
        #theme : journal
        #css : 628notes.css
        code_folding: hide
        #lib_dir : deps
        self_contained : true
        fig_width: 8
        fig_height: 6
---

@@

sgtype <- opts_knit$get("rmarkdown.pandoc.to")
sgstyle <- 'default'
colors <-  scale_color_solarized
colors_fill <- scale_fill_solarized
rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
source(paste(rootdir,"cases_and_policies/R/exploratory.R", sep="/"))
source(paste(rootdir,"cases_and_policies/R/dataprep.R",sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/varlabels.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/regprep.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/generatetables.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/bootstrap_felm.R", sep="/"))
```

@@

```{r testsmooth, cache=FALSE}
source("smoothtests.R")
```

@@

    tbl <- capture.output(stargazer(
        lapply(piy[1:4], function(x) x$reg),
        type="latex",
        dep.var.labels.include=FALSE,
        title=ylbl,
        # omit=omit,
        # omit.labels=omit.labels,
        column.labels=c(yvar),
        column.separate=c(length(piy[1:4])),
        # add.lines=list(c("$\\sum_j \\mathrm{Policy}_j$",
        #                  sapply(piy, function(x) printstars(x$peff[1], x$peff[2]))),
        #                c("",
        #                  sprintf("(%.3f)",sapply(piy, function(x) x$peff[2])))
        #                ),
        omit.stat=c("f", "ser"), model.names=FALSE,
        no.space=TRUE,
        column.sep.width="1pt",
        df=FALSE, header=FALSE,
        model.numbers=TRUE))
    tbl <- relabel(tbl)
    tbl <- gsub("Model (\\d)", "\\(\\1\\)", tbl)
    #tbl <- gsub("No","Yes", tbl)
    texfile <- sprintf("%s/tex/tables_and_figures/%s-piy.tex",rootdir,prefix)
    cat(paste(tbl[c(-1,-2,-3,-4, -length(tbl))], collapse="\n"), file=texfile)
```

## DML
```{r regsdml,  eval = FALSE, cache=FALSE, warning=FALSE, results='asis'}
